%\documentclass[journal]{IEEEtran}
\documentclass[12pt,draftcls,onecolumn]{IEEEtran}
%\usepackage{hyperref}
% show labels
%\usepackage[notref,notcite]{showkeys}
%\usepackage[T1]{fontenc}
%\usepackage[latin9]{inputenc}
%\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{graphicx}
%\usepackage{enumitem}
\usepackage{color}
%\usepackage{algorithm2e}
%\usepackage{appendix}
%\usepackage{algorithmic}
%\usepackage{program}




%\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
%\theoremstyle{plain}
%\newtheorem{thm}{Theorem}
%\theoremstyle{plain}
%\newtheorem{prop}[thm]{Proposition}
% \ifx\proof\undefined\
%   \newenvironment{proof}[1][\proofname]{\par
%     \normalfont\topsep6\p@\@plus6\p@\relax
%     \trivlist
%     \itemindent\parindent
%     \item[\hskip\labelsep
%           \scshape
%       #1]\ignorespaces
%   }{%
%     \endtrivlist\@endpefalse
%   }
%   \providecommand{\proofname}{Proof}
% \fi
%\theoremstyle{remark}
\newtheorem{rem}{Remark}
%\theoremstyle{definition}
\newtheorem{defn}{Definition}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{lem}{Lemma}

%\theoremstyle{plain}
%\newtheorem{lem}[thm]{Lemma}
%\theoremstyle{plain}
%\newtheorem{cor}[thm]{Corollary}
%
%\newtheorem{example}{Example}

%\makeatother

%\usepackage{babel}


\usepackage{my_macros}

\title{An Open-Loop Framework for Reach-Avoid Games}

\author{Zhengyuan Zhou, Haomiao Huang, Jerry Ding, Ryo Takei, and Claire~J.~Tomlin

\thanks{This work has been supported in part by NSF under CPS:ActionWebs
(CNS-931843), by ONR under the HUNT (N0014-08-0696) and
SMARTS (N00014-09-1-1051) MURIs and by grant N00014-12-1-0609, by AFOSR
under the CHASE MURI (FA9550-10-1-0567).}\vspace{-1cm}% <-this % stops a space
\thanks{Z.~Zhou, H.~Huang, J.~Ding, and C.~J.~Tomlin are with the Department of Electrical Engineering and Computer Sciences,
        University of California, Berkeley, CA, USA
        {\tt\small \{zhengyuan, haomiao, jding, tomlin\}@eecs.berkeley.edu}}        
%\thanks{R.~Takei is with ???,
%        ???
%        {\tt\small ??@??}}
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}


\begin{abstract}
We consider a game in which one or more attacking players attempt to reach a target while avoiding both obstacles and capture by opposing, defending players. 
Unlike pursuit-evasion games, in this reach-avoid game the players must consider both opposing players and the target.
This complexity makes finding solutions to such games difficult and computationally challenging, especially as the number of players grows.
We propose an approach to solving such games in an open-loop sense, where the players commit to their control actions prior to the beginning of the game.
This reduces the dimensionality of the required computations, and allows us to quickly compute feasible solutions in real time for domains with arbitrary obstacle topologies. 
We describe two such formulations, each of which is conservative towards one side, and derive algorithms based upon modified fast-marching methods (FMM) for efficiently computing their solutions.
The formulations and algorithms are discussed in detail, along with simulation results demonstrating their use in scenarios with complex obstacle geometries and player speed profiles.
\end{abstract}

\input{intro_modified.tex}
\input{related.tex}
\input{formulation.tex}
\input{theory_modified.tex}
\input{numerics.tex}
%\input{connection.tex}
\input{multiPlayer.tex}
\input{simulation.tex}
\input{conclusion.tex}

% bibliography
\bibliographystyle{IEEEtran}
\bibliography{refopenloop}

\end{document}
